\Title

### 2021-01-06 manuscript/manuscript.tex
Add text to manuscript

% Define title, authors, affiliations and DOI
% ===========================================
\newcommand{\Title}{
    Gradient-boosted equivalent sources
}
\newcommand{\Author}{
    S.R. Soler,
    L. Uieda
}
\newcommand{\AuthorAffil}{
    {\large
        Santiago R. Soler$^{1,2}$,
        Leonardo Uieda$^{3}$
    }
    \\[0.4cm]
    {\small $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com)} \\
    {\small $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina} \\
    {\small $^{3}$Department of Earth, Ocean and Ecological Sciences, School of Environmental Sciences, University of Liverpool, UK} \\
}
\newcommand{\DOI}{
    doi:\href{https://doi.org/xxx.xxx/xxxxxx}{xxx.xxx/xxxxxx}
}
\newcommand{\DOILink}{
    \href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}
}

@@

A widely used method for interpolating gravity and magnetic data
is the equivalent sources technique (also known as equivalent layer, radial
basis functions, or Green's functions interpolation), first introduced by
\citet{dampney1969}.
It consists in fitting a model of elementary sources to the data and using this
model to predict new data values.
Besides interpolation, equivalent sources have been used for
reduction-to-the-pole of magnetic data
\citep{silva1986, nakatsuka2006, guspi2009}, upward
continuation \citep{emilia1973, li2010}, joint processing of gravity gradient
data \citep{barnes2011}, modelling the lithospheric magnetic field
\citep{kother2015}, recovering the magnetic induction vector from
total-field magnetic anomalies \citep{li2020}, and more.

Many variants of the equivalent sources technique have been proposed, often
attempting to obtain faster or more accurate solutions.
The key factors that vary between them are: (i) the type of source, (ii)
the location of the sources, and (iii) the solution strategy.
The type of source is most commonly a point mass for gravity or dipole for
magnetics \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
However, right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019,
li2020} and tesseroids \citep{bouman2016} have also been used successfully.
In fact, even point sources with a simple inverse distance function, instead of
actual gravity or magnetic fields, can be used as
equivalent sources \citep{cordell1992}.
The sources are often distributed on a regular grid at a constant depth
\citep[e.g.,~][]{leao1989, barnes2011, oliveira2013}
or placed beneath each data point \citep[e.g.,~][]{cordell1992, siqueira2017}.
The model is usually estimated through damped least-squares, which imposes a
heavy computational load when the number of data points is large (e.g.,
airborne and satellite surveys).
To reduce the computational load, \citet{mendonca1994} built the solution
iteratively by incorporating one data point at a time using the ``equivalent
data concept''.
\citet{leao1989} processed the input data using a moving window, only fitting the
data inside the window and predicting observations at the center of the window.
\citet{li2010} and \citet{barnes2011} apply different operations to generate a
sparse representation of the sensitive matrix (respectively, wavelet
compression and quadtree discretization), which significantly improves the
speed of the least-squares solution.
\citet{oliveira2013} parametrized the equivalent layer as a piecewise bivariate
polynomial function, reducing the number of parameters in the solution.
\citet{siqueira2017} developed an iterative solution in which the sensitivity
matrix is transformed into a diagonal matrix with constant terms through the
``excess mass criterion''.
\citet{jirigalatu2019} applied the Gauss-FFT method to speed up the forward
modelling operations and solved the least-squares problem using steepest
descent to avoid calculating the Hessian matrix and solving linear systems.

@@

\noindent in which
$\mathbf{p}$ and $\mathbf{q}_j$ are position vectors in a 3D Cartesian space,
$c_j$ is a scalar coefficient related to the point source located at
$\mathbf{q}_j$,
and $\lVert \cdot \rVert$ represents the $\text{L}_2$ norm.
The horizontal and vertical distribution of sources is discussed in section~\ref{sec:source_distribution}.

@@

\subsection{Damped least-squares solution}
\label{sec:eql_inversion}

@@

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.
In practice, we find that suitable $\lambda$ values fall between $10^{-8}$ and
$10^{-1}$, irrespective of the dataset, and that results are mostly sensitive
to order-of-magnitude changes in $\lambda$.

@@

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (see section \ref{sec:source_distribution} for details).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that fall inside
    the respective window.
    Since the windows overlap, the total number of sources
    from all sets will be greater than $M$.
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

@@

To improve the convergence of the algorithm, \citet{friedman2002} suggests
introducing randomness into the fitting process. We achieve this by randomizing
the order in which the $K$ windows are used in the gradient boosting algorithm.

The $\mathbf{A}_k$ matrices have only $N \times M_k$ elements
(where $M_k$ is the number sources on the $k-$th window), which can be
considerably smaller than the $N \times M$ elements of $\mathbf{A}$.
Therefore, the gradient boosting method allows us to fit
equivalent source models that would produce Jacobian matrices that are larger
than the available computer memory.
Furthermore, we can increase or decrease the size of the overlapping windows as
needed depending on the number of sources in the model and the available
computer memory.

We can improve the efficiency of the algorithm further by using only the $N_k$ data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit} of
algorithm~\ref{alg:gradient_boosting}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}
of algorithm~\ref{alg:gradient_boosting}).
By doing so, we can reduce the size of the Jacobian matrix further to $N_k
\times M_k$ elements.
The forward modeling operation performed in step \ref{alg:predicted} can be
done by a summation (equation~\ref{eq:forward-sum})
instead of a matrix-vector product, which allows us to avoid computing and
storing the larger $N \times M_k$ Jacobian at any point.
Algorithm~\ref{alg:gradient_boosting_window} incorporates these changes and is
the final \textit{gradient-boosted equivalent source algorithm}.

@@

    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{d}_k$
    \;
  }
  \BlankLine
  \setstretch{1}
  \caption{Gradient-boosted equivalent source algorithm.}
  \label{alg:gradient_boosting_window}
\end{algorithm}

@@

\subsection{Location of sources}
\label{sec:source_distribution}

The ideal number of sources and their locations, both horizontally and
vertically, has been debated since the inception of the equivalent sources
technique with \citet{dampney1969}.
The choices made regarding these parameters can play an important role on the
accuracy of the predictions and the computational resources needed to estimate
the source coefficients.
An ideal distribution of sources should simultaneously be able to reproduce the
measured data on the survey points, make accurate predictions on non-surveyed
locations, and minimize the required computational resources.

A large number of evenly distributed sources along the survey region are
capable of reproducing the observed data.
Nevertheless, the computational load can be prohibitive and such
underdetermined problems are prone to overfiting the data, leading to poor
predictive power when interpolating and extrapolating.
On the other hand, using few sources will reduce the computational requirements
but the model may be incapable of reproducing the full spectral content of the
measured data.

Particular survey characteristics also play a role in the choice of equivalent
source distribution.
In a ground survey, observations are usually located along irregular paths and
scattered points.
The coverage of the survey region is often uneven, leaving large areas without
any observation.
On the other hand, observations from airborne surveys are located along almost
straight and closely spaced flight lines.
Measurements are usually taken at a high temporal frequency, leading to the
observation points along the flight lines that are several times closer to each
other than the flight line spacing.
This creates a bias in the sampling, which can cause aliasing artifacts in
gridded products.

\subsubsection{Horizontal source layouts}

The most widely used layouts for distributing equivalent sources horizontally
are:

\begin{enumerate}
  \item
    \emph{Regular grid}: a homogeneous distribution of point sources below the
    survey region at a constant depth. A padding region is often added to help
    reduce edge effects. In practice, it often leads to underdetermined problems
    since a large number of sources is required ($N<M$).
  \item
    \emph{Sources below data points}: one equivalent source is placed below each
    observation point at a given depth (often dependent on the distance to
    neighboring data points). Therefore, the number of sources is be equal to
    the number of observations ($N=M$).
\end{enumerate}

For ground surveys, the \emph{regular-grid} layout needs a sufficiently
small grid spacing to be able to fit the observed data.
This creates an unnecessarily large number of sources in areas where no
observations exist.
In contrast, the \emph{sources-below-data} layout is more likely to accurately
fit the observed data with many fewer sources, reducing the computational load.
But when applied to airborne surveys, the \emph{source-below-data} layout may
place an undesirably large number of sources along the flight paths.
This could lead to aliasing effects on the predicted values, such as the
stripes parallel to flight lines that are often observed when griding airborne
magnetic data.
In contrast, the \emph{regular-grid} layout can avoid this effect by evenly
distributing sources and using a continuous source layer (e.g.,
right-rectangular prisms or tesseroids).

We propose a new way of distributing equivalent sources horizontally that could
simultaneously reduce the computational load and mitigate some of the drawbacks
of existing layouts.
In the \emph{block-averaged sources} layout,
point sources are placed in the average
position of data points that fall within specified spatial blocks
(Fig.~\ref{fig:block-averaged-sources}).
This is done by:

\begin{enumerate}
    \item Dividing the survey region into rectangular blocks of equal size.
    \item Computing the median horizontal position of the observation points
      that fall inside each block. Blocks without any observation point are
      omitted.
    \item Assign one point source to the median horizontal position calculated
      in step 1.
\end{enumerate}

The number of sources created by this new layout will be less than the number
of observations if the block size is chosen appropriately (i.e., making sure
that blocks are large enough to contain more than a single data point).
The overdetermined problem that arises from this layout has a lower
computational load and is less prone to overfiting the data since the model
complexity is lower.
Moreover, the block averaging process can balance the spacing between sources
along a flight line and between adjacent lines, helping to reduce aliasing
effects in generated grids.

@@

\section{Performance of gradient-boosted equivalent sources}

@@

\subsection{Window size}
\label{sec:window_size}

@@

Using the best set of parameters for each window size, we registered the
achieved RMS against the values of the target grid and the time needed to fit
the sources coefficients.
In order to avoid any errors introduced by the way windows are shuffled, the
RMS for each window size was obtained as the mean RMS achieved by using
different random seeds.

\subsection{Overlapping}

@@

Using the best set of parameters for each overlap, we registered the achieved
RMS against the values of the target grid and the time needed to fit the
sources coefficients.
The RMS was obtained as the mean RMS achieved by using different random seeds
as we did on~\ref{sec:window_size}.

>>>>

% Define title, authors, affiliations and DOI
% ===========================================
\newcommand{\Title}{
    Gradient boosted equivalent sources
}
\newcommand{\Author}{
    S.R. Soler,
    L. Uieda
}
\newcommand{\AuthorAffil}{
    {\large
        Santiago R. Soler$^{1,2}$,
        Leonardo Uieda$^{3}$
    }
    \\[0.4cm]
    {\small $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com)} \\
    {\small $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina} \\
    {\small $^{3}$Department of Earth, Ocean and Ecological Sciences, School of Environmental Sciences, University of Liverpool, UK} \\
}
\newcommand{\DOI}{
    doi:\href{https://doi.org/xxx.xxx/xxxxxx}{xxx.xxx/xxxxxx}
}
\newcommand{\DOILink}{
    \href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}
}

@@

A widely used method for interpolating gravity and magnetic data
is the equivalent source technique (also known as equivalent layer, radial
basis functions, or Green's functions interpolation), first introduced by
\citet{dampney1969}.
It consists in fitting a model of elementary sources to the data and using this
model to predict new data values.
Besides interpolation, equivalent sources have been used for
reduction-to-the-pole of magnetic data
\citep{silva1986, nakatsuka2006, guspi2009}, upward
continuation \citep{emilia1973, li2010}, joint processing of gravity gradient
data \citep{barnes2011}, modelling the lithospheric magnetic field
\citep{kother2015}, recovering the magnetic induction vector from
total-field magnetic anomalies \citep{li2020}, and more.

Many variants of the equivalent source technique have been proposed, often
attempting to obtain faster or more accurate solutions.
The key factors that vary between them are: (i) the type of source, (ii)
the location of the sources, and (iii) the solution strategy.
The type of source is most commonly a point mass for gravity or dipole for
magnetics \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
However, right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019,
li2020} and tesseroids \citep{bouman2016} have also been used successfully.
In fact, even point sources with a simple inverse distance function, instead of
actual gravity or magnetic fields, can be used as
equivalent sources \citep{cordell1992}.
The sources are often distributed on a regular grid at a constant depth
\citep[e.g.,~][]{leao1989, barnes2011, oliveira2013}
or placed beneath each data point \citep[e.g.,~][]{cordell1992, siqueira2017}.
The model is usually estimated through damped least-squares, which imposes a
heavy computational load when the number of data points is large (e.g.,
airborne and satellite surveys).
To reduce the computational load, \citet{mendonca1994} built the solution
iteratively by incorporating one data point at a time using the ``equivalent
data concept''.
\citet{leao1989} processed the input data using a moving window, only fitting the
data inside the window and predicting observations at the center of the window.
\citet{li2010} and \citet{barnes2011} apply different operations to generate a
sparse representation of the sensitive matrix (respectively, wavelet
compression and quadtree discretization), which significantly improves the
speed of the least-squares solution.
\citet{oliveira2013} parametrized the equivalent layer as a piecewise bivariate
polynomial function, reducing the number of parameters in the solution.
\citet{siqueira2017} developed an iterative solution in which the sensitivity
matrix is transformed into a diagonal matrix with constant terms through the
``excess mass criterion''.
\citet{jirigalatu2019} applied the Gauss-FFT method to speed up the forward
modelling operations and solved the least-squares problem using steepest
descent to avoid calculating the Hessian matrix and solving linear systems.

@@

\noindent in which
$\mathbf{p}$ and $\mathbf{q}_j$ are position vectors in a 3D Cartesian space,
$c_j$ is a scalar coefficient related to the point source located at
$\mathbf{q}_j$,
and $\lVert \cdot \rVert$ represents the $\text{L}_2$ norm.

@@

\subsection{Damped least-squares solution}
\label{sec:eql-inversion}

@@

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.

@@

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (see section \ref{sec:source-distribution} for details).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that fall inside
    the respective window.
    Since the windows overlap, the total number of sources
    from all sets will be greater than $M$.
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

@@

To improve the convergence of the algorithm, \citet{friedman2002} suggests that
introducing randomness into the fitting process. We achieve this by randomizing
the order in which the $K$ windows are used in the gradient boosting algorithm.

The $\mathbf{A}_k$ matrices have only $N \times M_k$ elements
(where $M_k$ is the number sources on the $k-$th window), which can be
considerably smaller than the $N \times M$ elements of $\mathbf{A}$.
Therefore, the gradient boosting method allows us to fit
equivalent sources models that would produce Jacobian matrices that are larger
than the available computer memory.
Furthermore, we can increase or decrease the size of the overlapping windows as
needed depending on the number of sources in the model and the available
computer memory.

We can improve the efficiency of the algorithm further by using only the $N_k$ data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit} of
algorithm~\ref{alg:gradient_boosting}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}
of algorithm~\ref{alg:gradient_boosting}).
By doing so, we can reduce the size of the Jacobian matrix further to $N_k
\times M_k$ elements.
The forward modeling operation performed in step \ref{alg:predicted} can be
done by a summation (equation~\ref{eq:forward-sum})
instead of a matrix-vector product, which allows us to avoid computing and
storing the larger $N \times M_k$ Jacobian at any point.
Algorithm~\ref{alg:gradient_boosting_window} incorporates these changes and is
the final \textit{gradient boosted equivalent source algorithm}.

@@

    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{d}_k$
    \;
  }
  \BlankLine
  \setstretch{1}
  \caption{ Gradient boosted equivalent source algorithm. }
  \label{alg:gradient_boosting_window}
\end{algorithm}

@@

\subsection{Source distributions}
\label{sec:source-distribution}

How to choose how many sources to use and where to locate them are not
trivial decisions that play an important role on the accuracy of the
predictions and the computational resources needed to fit the sources'
coefficients.

The chosen distribution of sources should simultaneously reproduce the measured
data on the survey points and be able to make accurate predictions of the
measured harmonic field on non observed locations.

A high number of sources homogeneously distributed on the survey region are
capable of reproducing the observed data. Nevertheless, too many sources will
make the Jacobian matrix too large, what could introduce computational problems
like the inability of storing the matrix on memory or a high computational time
needed to fit the sources' coefficients.
On the other hand, using very few sources will undoubtedly reduce the memory
needs and lower the computational time when fitting the sources' coefficients.
Nevertheless, it could be incapable of making accurate predictions or even
reproducing the measured data if the number of sources is too low.

The choice of the source distribution could also depend on the characteristic
of the survey and how the observation points are distributed on the region.
A ground survey usually consists in observation points located along irregular
paths plus some possible scattered points.
The survey region is usually heterogeneously covered, leaving areas without any
observation.
On the other hand, an airborne survey consists in observation points located
along almost straight flight lines. The measurements are usually taken at
a high frequency, so the observation points along the flight lines are very
close to each other.
This creates an anisotropy on the observation points: there are much more
observation points along the flight lines directions.

The most widely used source distributions are: a regular grid of point sources
and one point source beneath each observation point.

The \emph{regular grid} creates an homogeneous distribution of point sources
below the surveyed region.
The distance between sources is controlled by the grid spacing parameter.
Keeping the boundaries of the grid constant, reducing the spacing increases the
number of sources.

The \emph{source below data} layout locates one source below each
observation point, therefore the number of sources will be equal to the number
of data points.

When working with ground surveys, the \emph{regular grid} needs the grid
spacing to be sufficiently small so observed values can be accurately
reproduced by the source distribution.
This will create too many sources on areas where no observation has been
carried out.
In contrast, the \emph{source below data} layout is more likely to accurately
fit the observed data with much less sources, reducing the computational load
to fit the equivalent sources' coefficients.

When working with airborne surveys, the \emph{source below data} may
generate an anisotropic distribution of sources by locating too many sources
along the flight paths.
It could lead to unwanted aliases on the predicted values.
In contrast, the \emph{regular grid} won't generate aliases by homogeneously
locating sources.

We propose a new source distribution that could simultaneously reduce the
computational load and remove the drawbacks of the preceding ones: the
\emph{block averaged sources}.
It consist in:

\begin{enumerate}
    \item Dividing the region in blocks of equal size. The size of the blocks
        is controlled by a \emph{spacing} parameter.
        (see Fig.~\ref{fig:block-averaged-sources}(a)-(b)).
    \item Computing the median location of the observation points that fall
        inside each block. Blocks without any observation point are ignored.
    \item Locating one point source below each block averaged coordinate.
        (see Fig.~\ref{fig:block-averaged-sources}(c)).
\end{enumerate}

The number of sources created by this new distribution will be less or equal to
the ones created by the \emph{source below data} and the \emph{regular
grid} with the same spacing.
Moreover, the sources are only located beneath populated blocks, so sources
will be concentrated on regions where data has been gathered and no anisotropic
distribution of sources will be generated.

@@

\section{Performance of gradient boosted equivalent sources}

@@

\subsection{Window size}
\label{sec:window-size}

@@

Using the best set of parameters for each window size, we registered the
achieved RMS against the values of the target grid and the time needed to fit
the sources coefficients (see Fig.~\ref{fig:gradient-boosted-window-size}a).
In order to avoid any errors introduced by the way windows are shuffled, the
RMS for each window size was obtained as the mean RMS achieved by using
different random seeds.

We have also registered the computational time needed to fit the
gradient-boosted equivalent sources for each window size and computed the ratio
between these times and the computational time needed to fit the non-boosted
equivalent sources (see Fig.~\ref{fig:gradient-boosted-window-size}b).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
    \caption{
        Gradient-boosted equivalent sources performance against window size.
        Window sizes are given as a fraction of the dimensions of the synthetic
        survey area.
        (a) Root-mean-squared error between predictions and target grid using
        non-boosted sources (orange dashed line) and gradient-boosted
        equivalent sources (blue dots) for different window sizes. Each RMS
        error is the mean of the RMS produced by the same set of parameters but
        with different random seeds.
        (b) Ratio between the computational times needed to fit the
        gradient-boosted and the non-boosted equivalent sources, respectively
        (the fitting time ratio for the non-boosted equivalent sources is
        therefore equal to one).
}
    \label{fig:gradient-boosted-window-size}
\end{figure}

From the results obtained from the comparison with the synthetic airborne
survey we can conclude that smaller windows generate less accurate predictions
than using larger ones and require significantly more computational time to fit
the sources.
The reduction of the accuracy might be due to an oversimplification of the
least-squares problem, and the increase of the computational time might be
generated by the great number of iterations required to fit the sources.
As the windows gets larger, the accuracy starts increasing because more data
points are included into the fitting process of the source coefficients, while
the fitting process takes less time due to a reduction of the number of
iterations.
For very large windows, both accuracy and fitting time are almost constant.

In comparison with the non-boosted equivalent sources, we can see that the
gradient-boosted ones produce slightly less accurate results due to not being
able to achieve the global minimum of the least-squares problem, but they
perform faster.

THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?

When using gradient-boosted equivalent sources we can conclude that we want to
maximize the window size as much as possible.
The only limitation to do so is to generate Jacobian matrices larger than the
available memory.
Therefore we recommend using the largest window that generates Jacobian
matrices that could fit in the available memory.

\subsection{Amount of overlap}

@@

Using the best set of parameters for each overlap, we registered the achieved
RMS against the values of the target grid and the time needed to fit the
sources coefficients.
The RMS was obtained as the mean RMS achieved by using different random seeds
as we did on~\ref{sec:window-size}.

We have also computed the fitting time ratio for each overlap, in a similar way
we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
    \caption{
        Gradient-boosted equivalent sources performance against amount of
        overlap.
        (a) Root-mean-squared error between predictions and target grid using
        non-boosted sources (orange dashed line) and gradient-boosted
        equivalent sources (blue dots) for different amount of overlap. Each
        RMS error is the mean of the RMS produced by the same set of parameters
        but with different random seeds.
        (b) Ratio between the computational times needed to fit the
        gradient-boosted and the non-boosted equivalent sources, respectively
        (the fitting time ratio for the non-boosted equivalent sources is
        therefore equal to one).
    }
    \label{fig:gradient-boosted-overlap}
\end{figure}

From the results obtained we can conclude that a lower values of overlap
generates less accurate results, while a higher overlap increases the
computational time required for fitting the source coefficients due to the
significant increment of the number of overlapping windows.

We found that overlaps less than 40\% produce very inaccurate predictions in
comparison with the non-boosted equivalent sources, while values larger that
80\% produce predictions with almost the same level of accuracy as the latter.
Nevertheless, overlap values larger that 70\% takes significantly more
computational time to fit the source coefficients.

THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?

We can then conclude that using overlap values between 40\% and 70\% generate
a balance between predictions accuracy and computational time needed to fit the
source coefficients.
This corroborates that our naive choice of 50\% is good enough for producing
accurate predictions in reasonable times.
